### 2024-05-10 article.tex
everything aligned right now but the cm,accuracy and loss for the audio model are now in the last page

\begin{figure*}[hbt]
	\centering
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/accuracy_vision_model.png}
		\caption{Accuracy of Vision Model on Train and Test Data}
		\label{accuracy-vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/loss_vision.png}
		\caption{Loss of Vision Model on Train and Test Data}
		\label{loss-vision}
	\end{minipage}
\end{figure*}
\clearpage

@@

The audio model was also created with EfficientNetB0 as its base for transfer learning after feature extraction done with MFCC Transform which was again transformed as explained in Section 4.3 for input compatibility with EfficientNetB0.
\par
We were able to achieve an accuracy of 90.39\% and an F1-Score of 88.1 on the test dataset. The batch size of 64 was chosen to increase the training pace. The size of test size of each class is 30.
\par
The following table shows various metrics of the audio model:
\vspace{3cm}

\begin{center}
	\captionof{table}{Audio Model Metrics}
	\begin{tabular}{ |c|c|c| }
		\hline
		\textbf{Parameters}      & \textbf{Metrics}          \\
		\hline
		Batch Size               & 64                        \\
		\hline
		Epochs                   & 15                        \\
		\hline
		Pretrained Model         & EfficientNetB0            \\
		\hline
		Weights                  & ImageNet                  \\
		\hline
		Learning Rate            & 0.0001                    \\
		\hline
		Weight Decay             & 0                         \\
		\hline
		Loss Function            & Categorical Cross Entropy \\
		\hline
		Optimizer                & Adam                      \\
		\hline
		Total Parameters         & 4,037,011                 \\
		\hline
		Trainable Parameters     & 4,037,011                 \\
		\hline
		Non-Trainable Parameters & 0                         \\
		\hline
	\end{tabular}

\end{center}
\clearpage
The confusion matrix on the test dataset:
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{Graphics/audio.png}
	\caption{Confusion Matrix for Audio Model on test data}
	\label{fig:enter-label}
\end{figure}

\clearpage
\par
We see a similar pattern as seen in the vision model here too in the audio model with similar featured data being mislabeled.
The figures below show the training and test accuracy as well as loss for the audio model:
\par
\begin{figure}[h]

	\centering
	\includegraphics[scale=0.6]{Graphics/audio_accuracy.png}
	\caption{Training and Test Accuracy of Audio Model}
	\includegraphics[scale=0.6]{Graphics/audio_loss.png}
	\caption{Training and Test Loss of Audio Model}

	\label{fig:enter-label}
\end{figure}

>>>>

\begin{figure*}[hbt]
	\centering
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/accuracy_vision_model.png}
		\caption{Accuracy of Vision Model on Train and Test Data}
		\label{accuracy-vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/loss_vision.png}
		\caption{Loss of Vision Model on Train and Test Data}
		\label{loss-vision}
	\end{minipage}
\end{figure*}

\clearpage

@@

The audio model was also created with EfficientNetB0 as its base for transfer learning after feature extraction done with MFCC Transform which was again transformed as explained in Section 4.3 for input compatibility with EfficientNetB0.
\par
We were able to achieve an accuracy of 90.39\% and an F1-Score of 88.1 on the test dataset. The batch size of 64 was chosen to increase the training pace. The size of test size of each class is 30.
\par
The following table shows various metrics of the audio model:

\begin{center}
	\captionof{table}{Audio Model Metrics}
	\begin{tabular}{ |c|c|c| }
		\hline
		\textbf{Parameters}      & \textbf{Metrics}          \\
		\hline
		Batch Size               & 64                        \\
		\hline
		Epochs                   & 15                        \\
		\hline
		Pretrained Model         & EfficientNetB0            \\
		\hline
		Weights                  & ImageNet                  \\
		\hline
		Learning Rate            & 0.0001                    \\
		\hline
		Weight Decay             & 0                         \\
		\hline
		Loss Function            & Categorical Cross Entropy \\
		\hline
		Optimizer                & Adam                      \\
		\hline
		Total Parameters         & 4,037,011                 \\
		\hline
		Trainable Parameters     & 4,037,011                 \\
		\hline
		Non-Trainable Parameters & 0                         \\
		\hline
	\end{tabular}
\end{center}
We see a similar pattern as seen in the vision model. Here too in the audio model with similar featured data being mislabeled. Figure \ref{accuracy-audio} and Figure \ref{loss-audio} shows the accuracy and loss of audio model respectively on test data. Figure \ref{cm_audio} shows confusion matrix for audio model on test dataset.

\begin{figure*}[hbt]
	\centering
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/audio_accuracy.png}
		\caption{Accuracy of Audio Model on Train and Test Data}
		\label{accuracy-audio}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/audio_loss.png}
		\caption{Loss of Audio Model on Train and Test Data}
		\label{loss-audio}
	\end{minipage}
\end{figure*}

\begin{figure*}[t] % Use figure* for spanning both columns
	\centering
	\begin{minipage}{\textwidth} % Use minipage to ensure the figure spans the whole width
		\includegraphics[scale=0.4]{Graphics/audio_cm.png} % Replace example-image with your actual image file
		\caption{Confusion Matrix for Audio Model on test data}
		\label{cm_audio}
	\end{minipage}
\end{figure*}
